Millions of Type Errors

### 2023-09-11 programming23/paper.tex
te fs agree/disagree
type error popularity by mode

\begin{table}[t]
  %% NOTE: looks the same when restricted to modules
  TODO recompute split by mode : te-editrange-ss-nocheck.rktd etc

  \begin{tabular}{l@{~~}l}
    \begin{tabular}[t]{lr}
      \code{SyntaxError} & 60.79\% \\
      \code{UnknownSymbol} & 27.34\% \\
      \code{UnknownProperty} & 4.08\% \\
      \code{TypeMismatch} & 1.92\% \\
      \code{UnknownRequire} & 1.40\% \\
      \code{CountMismatch} & 1.08\% \\
      \code{OptionalValueAccess} & 0.99\% \\
      \code{GenericError} & 0.93\% \\
      \code{CannotExtendTable} & 0.21\% \\
      \code{UnknownPropButFoundLikeProp} & 0.20\% \\
      \code{FunctionExitsWithoutReturning} & 0.16\% \\
      \code{ExtraInformation} & 0.14\% \\
      \code{CannotInferBinaryOperation} & 0.14\% \\
      \code{MissingProperties} & 0.13\% \\
      \code{ModuleHasCyclicDependency} & 0.10\% \\
      \code{IllegalRequire} & 0.09\% \\
      \code{NotATable} & 0.09\% \\
      \code{MissingUnionProperty} & 0.08\%
    \end{tabular} &
    \begin{tabular}[t]{lr}
      \code{CannotCallNonFunction} & 0.07\% \\
      \code{FunctionDoesNotTakeSelf} & 0.03\% \\
      \code{IncorrectGenericParameterCount} & 0.01\% \\
      \code{OnlyTablesCanHaveMethods} & 0.00\% \\
      \code{TypesAreUnrelated} & 0.00\% \\
      \code{DuplicateTypeDefinition} & 0.00\% \\
      \code{OccursCheckFailed} & 0.00\% \\
      \code{TypePackMismatch} & 0.00\% \\
      \code{FunctionRequiresSelf} & 0.00\% \\
      \code{DuplicateGenericParameter} & 0.00\% \\
      \code{InternalError} & 0.00\% \\
      \code{CodeTooComplex} & 0.00\% \\
      \code{DeprecatedApiUsed} & 0.00\% \\
      \code{NormalizationTooComplex} & 0.00\% \\
      \code{SwappedGenericTypeParameter} & 0.00\% \\
      \code{DynamicPropertyLookupOnClassesUnsafe} & 0.00\% \\
      \code{UnificationTooComplex} & 0.00\% \\
    \end{tabular}
  \end{tabular}
  \caption{Type error popularity}
  \label{t:type-error-count}
\end{table}

@@

% TODO ... somewhere ... te leq fs : use error-density
%%

\begin{figure}[t]
  TODO use 2 bars? ask a few similar questions?
  \includegraphics[width=0.8\columnwidth]{img/example-tefs.png}
  \caption{Are there fewer type errors than forcedstrict errors? Expect true always, but that is not the case.}
  \label{f:tefs}
\end{figure}

Seventh,

\begin{figure}[t]
TODO smaller

  \includegraphics[width=0.5\columnwidth]{img/example-compass.png}
  \caption{Are there fewer type errors than forcedstrict errors? Expect true always, but that is not the case.}
  \label{f:tefs}
\end{figure}

>>>>

\begin{table}[t]\centering
  %% NOTE: popularity looks similar when [over all records] vs. [restricted to module switch records]

  \begin{tabular}{ll}
    \mnonstrict{} & \mstrict{} \\
    \begin{tabular}[t]{l@{~}r}
      \code{UnknownSymbol} & \pct{62.13} \\
      \code{SyntaxError} & \pct{15.42} \\
      \code{UnknownProperty} & \pct{8.28} \\
      \code{UnknownRequire} & \pct{3.13} \\
      \code{TypeMismatch} & \pct{2.44} \\
      \code{CountMismatch} & \pct{2.26} \\
      \code{OptionalValueAccess} & \pct{2.07} \\
      \code{GenericError} & \pct{2.06} \\
      \code{UnknownPropButFoundLikeProp} & \pct{0.44} \\
      \code{CannotExtendTable} & \pct{0.42} \\
      \code{ExtraInformation} & \pct{0.32} \\
      \code{ModuleHasCyclicDependency} & \pct{0.23} \\
      \code{IllegalRequire} & \pct{0.20} \\
      \code{NotATable} & \pct{0.15} \\
      \code{CannotCallNonFunction} & \pct{0.15} \\
      \code{MissingProperties} & \pct{0.09} \\
      \code{FunctionExitsWithoutReturning} & \pct{0.07} \\
      \code{FunctionDoesNotTakeSelf} & \pct{0.07} \\
      \code{MissingUnionProperty} & \pct{0.02} \\
      \code{CannotInferBinaryOperation} & \pct{0.02} \\
      \code{OnlyTablesCanHaveMethods} & \pct{0.01} \\
      \code{DuplicateTypeDefinition} & {<\pct{0.01}} \\
      \code{TypesAreUnrelated} & {<\pct{0.01}} \\
    \end{tabular}
        &
    \begin{tabular}[t]{l@{~}r}
      \code{UnknownSymbol} & \pct{23.97} \\
      \code{TypeMismatch} & \pct{20.46} \\
      \code{UnknownProperty} & \pct{18.88} \\
      \code{SyntaxError} & \pct{9.31} \\
      \code{CannotInferBinaryOperation} & \pct{6.94} \\
      \code{MissingProperties} & \pct{4.04} \\
      \code{CountMismatch} & \pct{2.99} \\
      \code{OptionalValueAccess} & \pct{2.99} \\
      \code{FunctionExitsWithoutReturning} & \pct{2.99} \\
      \code{UnknownRequire} & \pct{2.37} \\
      \code{GenericError} & \pct{2.28} \\
      \code{NotATable} & \pct{1.32} \\
      \code{ExtraInformation} & \pct{0.35} \\
      \code{UnknownPropButFoundLikeProp} & \pct{0.26} \\
      \code{IncorrectGenericParameterCount} & \pct{0.18} \\
      \code{CannotCallNonFunction} & \pct{0.18} \\
      \code{IllegalRequire} & \pct{0.18} \\
      \code{ModuleHasCyclicDependency} & \pct{0.09} \\
      \code{CannotExtendTable} & \pct{0.09} \\
      \code{OccursCheckFailed} & \pct{0.09} \\
      \code{TypesAreUnrelated} & \pct{0.09} \\
    \end{tabular}
  \end{tabular}

  \caption{Type error popularity for \mnonstrict{} and \mstrict{} modes.
  In \mnocheck{}, \code{SyntaxError} accounts for \pct{100} of the error.}
  \label{t:type-error-count}
\end{table}

@@

\begin{figure}[t]\centering
  %% TODO
  %% - thin bars
  %% - colors for good , bad (disagree) , neutral
  \begin{tabular}{lll}
    \mnocheck{} & \mnonstrict{} & \mstrict{} \\
    \includegraphics[width=0.3\columnwidth]{img/compass-nocheck.pdf}
    &
    \includegraphics[width=0.3\columnwidth]{img/compass-nonstrict.pdf}
    &
    \includegraphics[width=0.3\columnwidth]{img/compass-strict.pdf}
  \end{tabular}
  \caption{FILL Are there fewer type errors than forcedstrict errors? Expect true always, but that is not the case.}
  \label{f:tefs}
\end{figure}

TODO individual sessions
